---
title: "Pickles"
author: "GenevieveMetcalf"
date: "10/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
require(tidyverse)
require(tigerstats)
```

# Introduction  

Form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

## SIMS~ARM Regression


```{r}
plot(SIMS~ARM,data=data)
```

This is a generic scatter plot of SIMS versus ARM  

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```


```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```


```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 

The greater the pounds of arm force(ARM), the greater the simulation(SIMS)  


```{r}
cor(SIMS~ARM,data=data)
```
This number is the correlation between SIMS and ARM force.
Correlation is a major of the linear association between two variables.

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
The equation is SIMS = -4.095160 + 0.054563 * ARM


```{r}
newData=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,newData,interval="prediction")
```


## SIMS~GRIP Regression

```{r}
plot(SIMS~GRIP,data=data)
```

This is a generic scatter plot of SIMS versus GRIP  

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=GRIP))
```

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

```{r}
basicNN + geom_point() + geom_smooth(method=lm)
``` 


The greater the pounds of grip force (GRIP), the greater simulation(SIMS)

```{r}
cor(SIMS~GRIP,data=data)
```
This number is the correlation between SIMS and GRIP force. 
Correlation is a major of the linear association between the two variables. 

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```
The equation is SIMS = -4.809675 + 0.045463 * GRIP

```{r}
newData=data.frame(GRIP=94,ARM=88)
predict.lm(model.2,newData,interval="prediction")
```

Fit is the predicted ARM score when you have the ARM strength of 94

the lwr and the upr are the 95% confidence interval for predicted SIMS score when the GRIP is 94

Comparing the two models, model1 and model 2,
Model1 (SIMS~ARM)has a slightly lower residual standard error score of 1.266 while model2 (SIMS~GRIP) scored at 1.295

Model1 (SIMS~ARM) has a higher adjusted r square score of 0.647 while model2 (SIMS~GRIP) scored a lower 0.4053.

Model2 is better because it has a higher residual standard than model1.

## SIMS~ARM+GRIP Regression



```{r}
model.3 <- lm(SIMS~ARM + GRIP,data=data)
summary.lm(model.3)
``` 


Model 3 seems to be the better model because the adjusted r square score than both model1 and model2, and also the residual standard error than model 1 or model2.


## Inferential Test

This inferential test is to compare models.

$H_0$: There is no difference in how well each model fits the data between the models (model1, model3)

$H_A$:There is a difference in how well each model fits the data between the models (model1, model3)  

```{r}
anova(model.1,model.3)
```
The p value is 0.00004994 which is very low.

We reject the null hypothesis because the P value is too low; There is a difference in model2 and model3; we have evidence that model3 is better than model2.

## MODEL COMPARISONS